---
title: "Crosswind LAM & Lester Results"
output: word_document
date: "2025-02-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi=300, fig.height = 5, fig.width = 7, message=FALSE, warning=FALSE)
```

## Estimating Mean Weight

Since fish sampling occurred during two events within different seasons and mimicking sport fishing under different regulations, size selectivity was observed to differ substantially between sampling events.  Because of this, a temporally stratified estimator was used to estimate mean weight for lake trout in Crosswind lake, given below, in which $b_{March}$ and $b_{June}$ represent the weights given to the March and June sampling events.  These were treated as equal in the analysis below.  The stratified estimators can be expressed as the following, for observations $i \in 1 ... n_k$ within season k:

$$\bar{W} = \frac{(b_{March} \times \bar{W}_{March}) + (b_{June} \times \bar{W}_{June})}{b_{March} + b_{June}}$$

and

$$\hat{V}(\bar{W}) = \frac{\left(b_{March}^2 \times \hat{V}(\bar{W}_{March})\right) + \left(b_{June}^2 \times \hat{V}(\bar{W}_{June})\right)}{(b_{March} + b_{June})^2}$$

in which

$$\bar{W}_k = \frac{\sum_{i=1}^{n_k}W_{k[i]}}{n_k}$$

and

$$\hat{V}(\bar{W}_k) = \frac{\sum_{i=1}^{n_k}(W_{k[i]}-\bar{W}_k)^2}{n_k(n_k-1)}$$

```{r}
library(tidyverse)

## per Corey email 9/4/2024
legal_nobait <- read_csv("BOF_2024/flat_data/legal_nobait.csv")

# ## the data I was sent before
# march_data <- read_csv("Analysis_2024/flat_data/March_Catch_Data.csv")[,-(14:21)]
# june_data <- read_csv("Analysis_2024/flat_data/June_Catch_Data.csv")
# 
# all_data <- data.frame(event = c(rep("March", nrow(march_data)),
#                                  rep("June", nrow(june_data))),
#                        FL = c(march_data$FL, june_data$FL),
#                        TL = c(march_data$FL, june_data$TL),
#                        weight_kg = c(march_data$kg, june_data$Kg),
#                        bait = c(march_data$Bait, june_data$Bait),
#                        gear = c(march_data$Gear, rep(NA, nrow(june_data))),
#                        technique = c(march_data$Technique, rep(NA, nrow(june_data))))
# 
# ## reconstructing legal_nobait from previous data - does it match?
# legal_nobait1 <- filter(all_data, (event == "March") | (event == "June" & bait == "N"))
# 
# (sort(legal_nobait$kg) == sort(legal_nobait1$weight_kg)) # %>% all
# ## it does match!



########### LAM inputs

area <- 3674#3717
log10_area <- log10(area)
log10_YP <- 0.72*log10_area + 0.6
YP_kg <- 10^log10_YP




########### estimating mean weight of harvest
season_weights <- c(0.5, 0.5)   # summer, then winter

# by season
season_Wbar <- tapply(legal_nobait$kg, legal_nobait$Season, mean)
season_n <- tapply(legal_nobait$kg, legal_nobait$Season, length)
season_varWbar <- tapply(legal_nobait$kg, legal_nobait$Season, var)/season_n
season_seWbar <- sqrt(season_varWbar)

# combined
Wbar <- sum(season_weights*season_Wbar)/sum(season_weights)
varWbar <- sum((season_weights^2)*season_varWbar)/(sum(season_weights)^2)
seWbar <- sqrt(varWbar)
```

For this purpose, the weights of `r season_n[2]` fish in the March sample were used, as well as `r season_n[1]` fish from the June sample that were not caught using bait.  The purpose of this was to provide representative samples of harvest that could occur during the Winter and Summer sport fishing seasons, under current regulations.

### Results

Mean weights by sample are summarized below.

```{r, results='asis'}
tab1 <- cbind(season_n, season_Wbar, season_seWbar)
colnames(tab1) <- c("n","Wbar_kg","SE(Wbar_kg)")
knitr::kable(tab1[2:1,], digits=3)
```

The mean weight of lake trout harvested from Crosswind lake was estimated as `r round(Wbar, 3)` kg (SE `r round(seWbar, 3)` kg) using stratification.

```{r}
p_winter <- seq(from=0, to=1, by=0.1)
est <- se <- NA*p_winter
for(i in seq_along(p_winter)) {
  season_weights1 <- c((1-p_winter[i]), p_winter[i])
  est[i] <- sum(season_weights1*season_Wbar)/sum(season_weights1)
  se[i] <- sum((season_weights1^2)*season_varWbar)/(sum(season_weights1)^2)
}
cilo <- est - 1.96*se
cihi <- est + 1.96*se

par(family="serif")
plot(p_winter, est, type="l", ylim=range(cilo, cihi),
       xlab="Seasonal Weights (Summer / Winter)", ylab="Est Mean Weight (kg)", xaxt="n")
  lines(p_winter, cilo, lty=2)
  lines(p_winter, cihi, lty=2)
  tlabs <- seq(from=0, to=1, by=0.2)
  axis(side=1, at=1-tlabs, labels=paste0(100*tlabs, "% / ", 100*(1-tlabs), "%"))
  legend("topleft", lty=1:2, legend=c("Estimate", "95% CI"))
```

\pagebreak

## LA Model

The LA model (Evans et al. 1991) was used to estimate yield potential of lake trout in Crosswind Lake as:

$$log_{10}(\hat{YP}) = 0.60 + 0.72log_{10}(A)$$

in which $\hat{YP}$ represents the estimated yield potential in kg biomass per year, and $A$ represents the lake area in hectares.

The unbiased yield potential (delta method; Seber 1982), in terms of number of lake trout, was estimated as:

$$\hat{YP}_n=\frac{\hat{YP}}{\bar{W}} + \frac{\hat{YP}}{\bar{W}^3}\hat{V}(\bar{W})$$

in which $\bar{W}$ represents the estimated mean weight of lake trout, using data from both the March and June sampling events.

The approximate variance was estimated as the following, treating estimated yield potential as constant:

$$\hat{V}_{naive}(\hat{YP}_n) = \frac{\hat{YP}^2}{\bar{W}^4}\hat{V}(\bar{W})$$

```{r}

# **THIS ^^^ IS NOT WHAT HAPPENED.**  I used Monte Carlo simulation to approximate the variance inherent to YP and bootstrapped the weight samples - still need to talk about this.
# 
# ```{r}
# # LAM assuming YP is known without error
# YP_n <- YP_kg/Wbar + YP_kg/(Wbar^3)*varWbar
# var_YP_n <- (YP_kg^2)/(Wbar^4)*varWbar
# se_YP_n <- sqrt(var_YP_n)
# ci_YP_n <- YP_n + c(-1,1)*1.96*se_YP_n
# ```
# 
# \pagebreak
# 
# ### Results - seasons equally weighted
# 
# Using this methodology and weighting the winter and summer samples equally, the yield potential in numbers of fish was estimated as `r round(YP_n, 2)` fish (SE `r round(se_YP_n, 2)`) fish, with an approximate 95% Wald confidence interval of (`r round(ci_YP_n[1], 2)` - `r round(ci_YP_n[2], 2)`), treating yield potential as known without error.  **It's unsatisfying, but I don't think it's honest to report these SE's / CI's.  Also in the fig below.**
# 
# ### Sensitivity to choice of weighting
# 
# To illustrate how inferences might differ under different seasonal weighting schemes, results were calculated for a sequence of weightings ranging from 100% Winter (0% Summer) to 0% Winter (100% Summer).  Results are displayed below.
# 
# ```{r}
# # ## investigating the effect of different weightings
# # possible_wts <- seq(.01, .99, by=.01)
# # ci_YP_n_all <- matrix(nrow=length(possible_wts), ncol=2)
# # YP_n_all <- rep(NA, length(possible_wts))
# # for(i in seq_along(possible_wts)) {
# #   season_weights <- c(possible_wts[i], 1-possible_wts[i])   # summer, then winter
# # 
# #   # by season
# #   season_Wbar <- tapply(legal_nobait$kg, legal_nobait$Season, mean)
# #   season_n <- tapply(legal_nobait$kg, legal_nobait$Season, length)
# #   season_varWbar <- tapply(legal_nobait$kg, legal_nobait$Season, var)/season_n
# #   season_seWbar <- sqrt(season_varWbar)
# # 
# #   # combined
# #   Wbar <- sum(season_weights*season_Wbar)/sum(season_weights)
# #   varWbar <- sum((season_weights^2)*season_varWbar)/(sum(season_weights)^2)
# #   seWbar <- sqrt(varWbar)
# # 
# #   # LAM assuming YP is known without error
# #   YP_n <- YP_kg/Wbar + YP_kg/(Wbar^3)*varWbar
# #   var_YP_n <- (YP_kg^2)/(Wbar^4)*varWbar
# #   se_YP_n <- sqrt(var_YP_n)
# #   ci_YP_n <- YP_n + c(-1,1)*1.96*se_YP_n
# # 
# #   YP_n_all[i] <- YP_n
# #   ci_YP_n_all[i,] <- ci_YP_n
# # }
# # plot(NA, xlim=0:1, ylim=range(ci_YP_n_all),
# #      ylab="YP_n", xlab="Seasonal Weights",
# #      xaxt="n")
# # lines(possible_wts, YP_n_all)
# # lines(possible_wts, ci_YP_n_all[,1], lty=2)
# # lines(possible_wts, ci_YP_n_all[,2], lty=2)
# # legend("topleft", lty=1:2, legend=c("Estimate", "95% CI"))
# # 
# # axis(side=1, at=seq(0, 1, by=0.2),
# #      labels = paste0(seq(0, 100, 20), "% / ",
# #                     seq(100, 0, -20), "%"))
# ```

```

### Incorporating uncertainty due to estimation in the Lake Area Model

It is important to recognize the variance due to prediction from the LAM.  The LA model reported by Evans et al. (1991) is expressed as a linear regression on the log-log scale, with an $R^2$ of 0.69 and n=43.  Sampling from the lake area data reported by Evans et al. and simulating YP values such that the estimated regression parameters are equivalent to those reported provides an approximate estimate of the model residual variance and thereby prediction variance for a new lake with the same area as Crosswind Lake.  

The previous analysis was repeated, using values of $\hat{YP}$ simulated using the prediction variance estimated for Crosswind Lake, and back-transformed to the natural scale.  

```{r}
# prediction variance of a new lake (Crosswind), on the log scale
predvarsim <- 0.09958763

nsim <- 100000

## vector of simulated YP (kg) of new lake, on the log scale
predlog10YP_kg <- rnorm(nsim, 0.6 + 0.72*log10(area), sqrt(predvarsim))

## back to natural scale
predYP_kg <- 10^predlog10YP_kg
# hist(predYP)

# the sampling variances of the weight samples are incorporated using bootstrapping!
# YP_sim <- rep(NA, nsim)
winter_boot_mn <- summer_boot_mn <- rep(NA, nsim)
for(i in 1:nsim) {
  # winter_boot <- sample(legal_nobait$kg[legal_nobait$Season == "Winter"], replace=TRUE)
  # summer_boot <- sample(legal_nobait$kg[legal_nobait$Season == "Summer"], replace=TRUE)
  winter_boot_mn[i] <- mean(sample(legal_nobait$kg[legal_nobait$Season == "Winter"], replace=TRUE))
  summer_boot_mn[i] <- mean(sample(legal_nobait$kg[legal_nobait$Season == "Summer"], replace=TRUE))

  # weight_winter <- 0.5
  # # weight_winter <- rbeta(1, 5, 5)
  # weight_summer <- 1 - weight_winter
  # 
  # Wbar <- (weight_winter * mean(winter_boot)) + (weight_summer * mean(summer_boot))
  # YP_sim[i] <- predYP_kg[i]/Wbar
}

weight_winter <- 0.5
# weight_winter <- rbeta(1, 5, 5)
weight_summer <- 1 - weight_winter

Wbar <- (weight_winter * winter_boot_mn) + (weight_summer * summer_boot_mn)
YP_sim <- predYP_kg/Wbar

# hist(YP_sim)
# mean(YP_sim)
# median(YP_sim)
# sd(YP_sim)
# 
# quantile(YP_sim, c(0.025, 0.975))
```

```{r}
# Incorporating the uncertainty due to estimation of the LAM and resampling the fish weights in each season yields a bootstrap mean and median of `r round(mean(YP_sim), 2)` and `r round(median(YP_sim), 2)` fish, respectively (SE `r round(sd(YP_sim), 2)` fish) and an approximate 95% confidence interval of (`r round(quantile(YP_sim, 0.025), 2)` - `r round(quantile(YP_sim, 0.975), 2)`).
```

\pagebreak

### LAM Results: incorporating model variance

```{r}
weighted_ests <- function(y_kg, season_weights = c(0.5, 0.5)) {
  # by season
  season_Wbar <- tapply(legal_nobait$kg, legal_nobait$Season, mean)
  season_n <- tapply(legal_nobait$kg, legal_nobait$Season, length)
  season_varWbar <- tapply(legal_nobait$kg, legal_nobait$Season, var)/season_n
  season_seWbar <- sqrt(season_varWbar)

  # combined
  Wbar <- sum(season_weights*season_Wbar)/sum(season_weights)
  varWbar <- sum((season_weights^2)*season_varWbar)/(sum(season_weights)^2)
  seWbar <- sqrt(varWbar)
  
  # assuming YP is known without error
  out <- list()
  out$y_n <- y_kg/Wbar + y_kg/(Wbar^3)*varWbar
  var_y_n <- (y_kg^2)/(Wbar^4)*varWbar
  out$se_y_n <- sqrt(var_y_n)
  out$ci_y_n <- out$y_n + c(-1,1)*1.96*out$se_y_n
  
  return(out)
}
# ests_null <- weighted_ests(y_kg = msy_null)
# ests_samp <- weighted_ests(y_kg = msy_samp)
# ests_mod <- weighted_ests(y_kg = msy_mod)
```

```{r}
p_winter <- seq(from=0, to=1, by=0.1)  # was 0.01 but this isn't needed
# YP_mat <- matrix(nrow=length(YP_sim), ncol=length(p_winter))
YP_ci_lo <- YP_ci_hi <- YP_est <- YP_se <- W_est <- SE_W_est  <- NA*p_winter
for(i in seq_along(p_winter)) {
  YP_sim_weighted <- predYP_kg/((p_winter[i] * winter_boot_mn) + ((1-p_winter[i]) * summer_boot_mn))
  xx <- weighted_ests(y_kg=YP_kg, season_weights = c((1-p_winter[i]), p_winter[i]))
  YP_ci_lo[i] <- quantile(YP_sim_weighted, 0.025)
  YP_ci_hi[i] <- quantile(YP_sim_weighted, 0.975)
  YP_est[i] <- xx$y_n#quantile(YP_sim_weighted, 0.5)
  YP_se[i] <- sd(YP_sim_weighted)
  W_est[i] <- (1-p_winter[i])*mean(legal_nobait$kg[legal_nobait$Season == "Summer"]) +
    p_winter[i]*mean(legal_nobait$kg[legal_nobait$Season == "Winter"])
  SE_W_est[i] <- sqrt(((1-p_winter[i])^2)*var(legal_nobait$kg[legal_nobait$Season == "Summer"])/sum(legal_nobait$Season == "Summer") +
    (p_winter[i]^2)*var(legal_nobait$kg[legal_nobait$Season == "Winter"])/sum(legal_nobait$Season == "Winter"))
}

### these will become table 6 and fig 4
tbl6 <-
  data.frame(`SW` = paste(100*(1-p_winter), 100*p_winter, sep="/"),
             W=W_est, SE_W=SE_W_est,
            YPn=YP_est, SE_YPn=YP_se, 
            lwr95_YPn=YP_ci_lo, upr95_YPn=YP_ci_hi)

```

```{r}
tbl6_naive <- tbl6
for(i in seq_along(p_winter)) {
  xx <- weighted_ests(y_kg=YP_kg, season_weights = c((1-p_winter[i]), p_winter[i]))
  tbl6_naive$YPn[i] <- xx$y_n
  tbl6_naive$SE_YPn[i] <- xx$se_y_n
  tbl6_naive$lwr95_YPn[i] <- xx$ci_y_n[1]
  tbl6_naive$upr95_YPn[i] <- xx$ci_y_n[2]
}
```

```{r}
plot_fig4 <- function(tab, cilim=0, ...) {
  par(family="serif")
  p_winter <- seq(from=0, to=1, length.out=nrow(tab))
  plot(p_winter, tab$YPn, type="l", ylim=range(cilim, tab$lwr95_YPn, tab$upr95_YPn), #ylim=range(0, tab$upr95_YPn),
       xlab="Seasonal Weights (Summer / Winter)", ylab="YP (n)", xaxt="n",...=...)
  lines(p_winter, tab$lwr95_YPn, lty=2)
  lines(p_winter, tab$upr95_YPn, lty=2)
  tlabs <- seq(from=0, to=1, by=0.2)
  axis(side=1, at=1-tlabs, labels=paste0(100*tlabs, "% / ", 100*(1-tlabs), "%"))
  legend("topright", lty=1:2, legend=c("Estimate", "95% CI"))
}
```

```{r}
knitr::kable(tbl6, digits=c(0,2,2,0,0,0,0))
```

```{r}
plot_fig4(tbl6)
```

\pagebreak

### LAM Results: treating LAM-estimated YP as known without error

```{r}
knitr::kable(tbl6_naive, digits=c(0,2,2,0,1,0,0))
```

```{r}
plot_fig4(tbl6_naive, cilim=400)
```

\pagebreak

## Lester Model

The Lester model (Lester et al. 2021) was used to estimate MSY (in kg biomass) using a stepwise approach. First the depth ratio (DR) of Crosswind Lake was calculated using:

$DR = \frac{D_{max}}{D_{mn}}$

where

$D_{max}$ = Maximum depth from bathymetric mapping (m)

$D_{mn}$ = Mean depth from bathymetric mapping (m)

Thermocline depth ($D_{th}$) was estimated using:

$D_{th} = 3.26 \times A^{0.109} \times D_{mn}^{0.213} \times e^{-0.0263T}$

where

*A* = surface area of Crosswind Lake (ha)

*T* = mean annual air temperature near Crosswind Lake ($^\circ$C)

The proportion of the lake volume in the hypolimnetic zone ($pV_{hy}$) was estimated using:

$pV_{hy} = \left(1-\frac{D_{th}}{D_{max}}\right)^{DR}$

The volume of the epibenthic zone  ($pV_{eb}$) was estimated using:

$pV_{eb} = e^{-4.63pV_{hy}}$

Habitat suitability (*S*) was summarized using:

$S = \frac{1}{1+e^{2.47+0.386T-16.8pV_{hy}}}$

Asymptotic length ($L_{\infty}$) and weight ($W_{\infty}$) of lake trout in Crosswind Lake was estimated 2 ways: using the Lester model (equations 13 and 14 below) and by using data collected from catch sampling.

Asymptotic length ($L_{\infty}$) was estimated within the Lester model using:

$L_{\infty} = 957 \times \left(1-e^{-0.14 \times (1+log_eA)}\right)$  **We did not do this.**

Asymptotic weight ($W_{\infty}$) was estimated within the Lester Model by converting asymptotic length ($L_{\infty}$) to weight using:

$W_{\infty} = \left(\frac{L_{\infty}}{451}\right)^{3.2}$  **We did not do this.**

An alternative method for estimating asymptotic weight ($W_{\infty}$) required taking the mean weight of the heaviest 10% of the fish weighed from the March and June sampling (Lester et al. 2021). This lake specific result was compared to, and possibly substituted for the results of equation 14.  Additionally, asymptotic weight was estimated using an integrated Bayesian model incorporating information from several Alaska lakes with lake trout **(Will write up methods & results soon!)**

Biomass density when a population is exploited and MSY ($B_{msy}$) was then estimated using:

$B_{msy}  = \frac{8.47 \times D_{mn} \times pV_{eb}  \times S }{W_{\infty}^{1.33}}$

Natural mortality rate of the population (M) was estimated using:

$M= \frac{0.26e^{0.021T + 0.0004T^2}}{W_{\infty}^{0.30}}$

**Lester estimates the 1.33 and 0.30 with se's of 0.17 and 0.04 respectively, which is kind of a big deal when propagated through.**

MSY for surface area ($MSY_{ha}$) was estimated using:

$MSY_{ha} = B_{msy} \times M$

MSY in terms of kg biomass was estimated using

$MSY = MSY_{ha} \times A$

MSY was then expressed in numbers of fish ($MSY_n$) using

$$MSY_n=\frac{MSY}{\bar{W}} + \frac{MSY}{\bar{W}^3}\hat{V}(\bar{W})$$

$$\hat{V}_{naive}(MSY_n) = \frac{MSY^2}{\bar{W}^4}\hat{V}(\bar{W})$$  

where

$\hat{W}$ = estimated mean weight of lake trout subject to harvest from Crosswind Lake.

### Incorporating uncertainty due to estimation in the Lester Model

$W_{\infty}$ was estimated using a Bayesian model incorporating all catch sampling from Crosswind Lake including some additional studies, as well as additional information from hierarchical modeling of relationships between age, length, and weight from 40 other lakes.  Estimation of $MSY_n$ within the Lester model is particularly sensitive to  $W_{\infty}$, therefore a robust estimate of asymptotic weight was critical, and any associated variance should be considered.

Lester et al. report standard errors associated with two parameters, namely the exponents of $W_{\infty}$ in equations XXX and XXX.  Since uncertainty about an exponent can be expected to dominate other sources of variance within the model, accounting for this can be expected to result in a reasonable estimate of minimum variance in $MSY_n$.

A minimum estimate of the variance in Lester model results for Crosswind Lake was accomplished by means of a combination of Markov Chain Monte Carlo (MCMC) sampling of $W_{\infty}$ and Monte Carlo simulation of the parameters in Equations XXX and XXX above, assuming mutually independent Normal distributions standard deviations equal to the standard errors reported by Lester et al.

```{r}
## here comes Lester stuff!
Temp <- -3 # direct input
A <- area  # carried from before
D_max <- 44.2 # direct input
D_mn <- 16.4 # 16.5  # direct input     - SHOULD BE 16.4 APPARENTLY
DR <- D_max/D_mn
D_th <- 3.26*(A^0.109)*(D_mn^0.213)*exp(-0.0263*Temp)
pV_hy <- (1-(D_th/D_max))^DR
pV_eb <- exp(-4.63*pV_hy)

# using Lester Winf
L_inf <- 957*(1-exp(-0.14*(1+log(A))))
W_inf_null <- (L_inf/451)^3.2

S <- 1/(1+exp(2.47+(0.386*Temp)-(16.8*pV_hy)))
B_msy <- 8.47*(D_mn*pV_eb*S)/(W_inf_null^1.33)
M <- 0.26*(exp((0.021*Temp)+(0.0004*(Temp^2))))/(W_inf_null^0.30)
msy_ha_null <- B_msy*M
msy_null <- msy_ha_null*area 

# using sampled Winf
W_inf_samp <- 6.35  # direct input
S <- 1/(1+exp(2.47+(0.386*Temp)-(16.8*pV_hy)))
B_msy <- 8.47*(D_mn*pV_eb*S)/(W_inf_samp^1.33)
M <- 0.26*(exp((0.021*Temp)+(0.0004*(Temp^2))))/(W_inf_samp^0.30)
msy_ha_samp <- B_msy*M
msy_samp <- msy_ha_samp*area   

load(file="W_inf_vec.Rdata")
W_inf_mod <- median(W_inf_vec)
S <- 1/(1+exp(2.47+(0.386*Temp)-(16.8*pV_hy)))
B_msy <- 8.47*(D_mn*pV_eb*S)/(W_inf_mod^1.33)
M <- 0.26*(exp((0.021*Temp)+(0.0004*(Temp^2))))/(W_inf_mod^0.30)
msy_ha_mod <- B_msy*M
msy_mod <- msy_ha_mod*area   
```

```{r}

# ### Results
# 
# Results were tabulated for three possible values of $W_{\infty}$, first as estimated within the Lester framework from lake area, then as estimated directly from the sample, then using the integrated Bayesian model.  
# 
# There is a surprising amount of discrepancy between asymptotic weight as estimated from lake area alone and as estimated from catch sampling, with fish tending to be larger than would be estimated from lake area alone.  This highlights the degree of variability actually present within the relationship between lake area and asymptotic weight, and by logical extension, the relationship between lake area and YP (from the LAM) or MSY (from the Lester model).  Note that there is reasonable agreement between YP (estimated from lake area alone) and 50% MSY, when asymptotic weight is estimated from lake area alone.
# 
# Point estimates are compared below, using 50/50 seasonal weighting for illustration.  **I'm not sure if this is correct after incorporating the Lester variance.**

```

```{r}
# comptable <- data.frame(Estimate=c("Lake Area", "Catch sampling", "Bayesian"),
#                         W_inf=c(W_inf_null, W_inf_samp, W_inf_mod),
#                         MSY=c(msy_null, msy_samp, msy_mod),
#                         MSY_n=c(ests_null$y_n, ests_samp$y_n, ests_mod$y_n),
#                         MSY_n_50=0.5*c(ests_null$y_n, ests_samp$y_n, ests_mod$y_n))
# knitr::kable(comptable, digits=c(0, 2, 0, 0, 0))
```

```{r}
# Lester again, with variance

load(file="W_inf_vec.Rdata")
nsim <- length(W_inf_vec)

# Temp <- -3 # direct input
# A <- area  # carried from before
# D_max <- 44.2 # direct input
# D_mn <- 16.5  # direct input
# DR <- D_max/D_mn
# D_th <- 3.26*(A^0.109)*(D_mn^0.213)*exp(-0.0263*Temp)
# pV_hy <- (1-(D_th/D_max))^DR
# pV_eb <- exp(-4.63*pV_hy)

# using Lester Winf
L_inf <- 957*(1-exp(-0.14*(1+log(A))))
W_inf_null <- (L_inf/451)^3.2

exponent1 <- rnorm(n=nsim, mean=1.33, sd=0.17)
exponent2 <- rnorm(n=nsim, mean=0.30, sd=0.04)

S <- 1/(1+exp(2.47+(0.386*Temp)-(16.8*pV_hy)))
B_msy <- 8.47*(D_mn*pV_eb*S)/(W_inf_null^exponent1)
M <- 0.26*(exp((0.021*Temp)+(0.0004*(Temp^2))))/(W_inf_null^exponent2)
msy_ha_null <- B_msy*M
msy_null <- msy_ha_null*area 

# using sampled Winf
W_inf_samp <- 6.35  # direct input
S <- 1/(1+exp(2.47+(0.386*Temp)-(16.8*pV_hy)))
B_msy <- 8.47*(D_mn*pV_eb*S)/(W_inf_samp^exponent1)
M <- 0.26*(exp((0.021*Temp)+(0.0004*(Temp^2))))/(W_inf_samp^exponent2)
msy_ha_samp <- B_msy*M
msy_samp <- msy_ha_samp*area   

W_inf_mod <- W_inf_vec # median(W_inf_vec)
S <- 1/(1+exp(2.47+(0.386*Temp)-(16.8*pV_hy)))
B_msy <- 8.47*(D_mn*pV_eb*S)/(W_inf_mod^exponent1)
M <- 0.26*(exp((0.021*Temp)+(0.0004*(Temp^2))))/(W_inf_mod^exponent2)
msy_ha_mod <- B_msy*M
msy_mod <- msy_ha_mod*area   
```

```{r}
tbl7 <- data.frame(`SW` = paste(100*(1-p_winter), 100*p_winter, sep="/"),
             W=tbl6$W, SE_W=tbl6$SE_W,
             MSY40=NA, MSY50=NA, MSY60=NA, MSY70=NA, MSY80=NA, MSY90=NA, MSY100=NA)
fig5_ci <- fig5_ci_naive <- data.frame(ci_lo=rep(NA, length(p_winter)), ci_hi=NA)
for(i in seq_along(p_winter)) {
  season_weights <- c(1-p_winter[i], p_winter[i])
  tbl7$MSY100[i] <- 
    weighted_ests(y_kg=median(msy_mod), season_weights=season_weights)$y_n
  msy_n_vec <- 0.5*msy_mod/(p_winter[i]*winter_boot_mn + (1-p_winter[i])*summer_boot_mn)
  fig5_ci$ci_lo[i] <- quantile(msy_n_vec, 0.025)
  fig5_ci$ci_hi[i] <- quantile(msy_n_vec, 0.975)
  fig5_ci_naive$ci_lo[i] <- weighted_ests(y_kg=0.5*median(msy_mod), season_weights=season_weights)$ci_y_n[1]
  fig5_ci_naive$ci_hi[i] <- weighted_ests(y_kg=0.5*median(msy_mod), season_weights=season_weights)$ci_y_n[2]
}
for(j in 4:9) {
  tbl7[,j] <- j/10*tbl7[,10]
}
```

```{r}
plot_fig5 <- function(est, ci, cilim=0, ...) {
  par(family="serif")
  p_winter <- seq(from=0, to=1, length.out=nrow(est))
  plot(p_winter, est$MSY50, type="l", ylim=range(cilim, ci),#ylim=range(0,ci),
       xlab="Seasonal Weights (Summer / Winter)", ylab="50% MSY (n)", xaxt="n",...=...)
  lines(p_winter, ci$ci_lo, lty=2)
  lines(p_winter, ci$ci_hi, lty=2)
  tlabs <- seq(from=0, to=1, by=0.2)
  axis(side=1, at=1-tlabs, labels=paste0(100*tlabs, "% / ", 100*(1-tlabs), "%"))
  legend("topright", lty=1:2, legend=c("Estimate", "95% CI"))
}
```

```{r}
plot_fig45 <- function(tab, est, ci, cilim=0, ...) {
  par(family="serif")
  p_winter <- seq(from=0, to=1, length.out=nrow(tab))
  plot(p_winter, tab$YPn, type="l", ylim=range(cilim, tab$lwr95_YPn, tab$upr95_YPn, ci),
       xlab="Seasonal Weights (Summer / Winter)", ylab="n fish", xaxt="n",col=2, lwd=2, ...=...)
  # lines(p_winter, tab$lwr95_YPn, lty=2)
  # lines(p_winter, tab$upr95_YPn, lty=2)
  polygon(x=c(p_winter, rev(p_winter)), y=c(tab$lwr95_YPn, rev(tab$upr95_YPn)), 
          border=NA, col=adjustcolor(2, alpha.f=.3))
  
  lines(p_winter, est$MSY50, col=4, lwd=2)
  polygon(x=c(p_winter, rev(p_winter)), y=c(ci$ci_lo, rev(ci$ci_hi)), 
          border=NA, col=adjustcolor(4, alpha.f=.3))
  
  tlabs <- seq(from=0, to=1, by=0.2)
  axis(side=1, at=1-tlabs, labels=paste0(100*tlabs, "% / ", 100*(1-tlabs), "%"))
  # legend("topright", lty=1:2, legend=c("Estimate", "95% CI"))
  legend("topright", border=c(2,4), fill=c(adjustcolor(2, alpha.f=.3), adjustcolor(4, alpha.f=.3)),
         legend=c("YP (LAM)", "50% MSY (Lester)"))
}
```

```{r}
p_msy <- seq(from=0.4, to=1, by=0.1)
tbl8 <- data.frame(perc_MSY=100*p_msy, MSY_n=NA, SE_MSY_n=NA, Lwr_95_CI=NA, Upr_95_CI=NA)
for(i in seq_along(p_msy)) {
  msy_n_vec <- p_msy[i]*msy_mod/(0.5*winter_boot_mn + 0.5*summer_boot_mn)
  tbl8$MSY_n[i] <- weighted_ests(y_kg=p_msy[i]*median(msy_mod), season_weights=rep(0.5,2))$y_n
  tbl8$SE_MSY_n[i] <- sd(msy_n_vec)
  tbl8$Upr_95_CI[i] <- quantile(msy_n_vec, 0.975)
  tbl8$Lwr_95_CI[i] <- quantile(msy_n_vec, 0.025)
}
```

```{r}
tbl8_naive <- tbl8
for(i in seq_along(p_msy)) {
  xx <- weighted_ests(p_msy[i]*median(msy_mod), season_weights=rep(0.5,2))
  tbl8_naive$SE_MSY_n[i] <- xx$se_y_n
  tbl8_naive$Upr_95_CI[i] <- xx$ci_y_n[2]
  tbl8_naive$Lwr_95_CI[i] <- xx$ci_y_n[1]
}
```

```{r}
plot_fig6 <- function(tab, ...) {
  par(family="serif")
  p_msy <- tab$perc_MSY
  plot(p_msy, tab$MSY_n, type="l", ylim=range(0,tab$Upr_95_CI),
       xlab="Percent of MSY", ylab="Fractional MSY (n)",...=...)
  lines(p_msy, tab$Lwr_95_CI, lty=2)
  lines(p_msy, tab$Upr_95_CI, lty=2)
  # tlabs <- seq(from=0, to=1, by=0.2)
  # axis(side=1, at=1-tlabs, labels=paste0(100*tlabs, "% / ", 100*(1-tlabs), "%"))
  legend("topleft", lty=1:2, legend=c("Estimate", "95% CI"))
}
```

\pagebreak

### Lester Results: incorporating Lester variance (within-model, and asymptotic weight)

```{r}
plot_fig5(est=tbl7, ci=fig5_ci)
```

```{r}
knitr::kable(tbl7, digits=c(0,2,2,rep(0,7)))
```

\pagebreak

```{r}
knitr::kable(tbl8, digits=0)
```

```{r}
plot_fig6(tab=tbl8)
```

\pagebreak

### Lester Results: treating Lester-estimated MSY as known without error

```{r}
plot_fig5(est=tbl7, ci=fig5_ci_naive, cilim=200)
```

```{r}
knitr::kable(tbl7, digits=c(0,2,2,rep(0,7)))
```

\pagebreak

```{r}
knitr::kable(tbl8_naive, digits=c(0,0,1,0,0))
```

```{r}
plot_fig6(tab=tbl8_naive)
```

\pagebreak

### Illustrating the sensitivity of Lester inferences to $W_{\infty}$

```{r}
## here comes Lester stuff!
# Temp <- -3 # direct input
# A <- area  # carried from before
# D_max <- 44.2 # direct input
# D_mn <- 16.5  # direct input
# DR <- D_max/D_mn
# D_th <- 3.26*(A^0.109)*(D_mn^0.213)*exp(-0.0263*Temp)
# pV_hy <- (1-(D_th/D_max))^DR
# pV_eb <- exp(-4.63*pV_hy)

# using Lester Winf
L_inf <- 957*(1-exp(-0.14*(1+log(A))))
W_inf_null <- (L_inf/451)^3.2

S <- 1/(1+exp(2.47+(0.386*Temp)-(16.8*pV_hy)))
B_msy <- 8.47*(D_mn*pV_eb*S)/(W_inf_null^1.33)
M <- 0.26*(exp((0.021*Temp)+(0.0004*(Temp^2))))/(W_inf_null^0.30)
msy_ha_null <- B_msy*M
msy_null <- msy_ha_null*area 

# defining a sequence of trial values of W_inf
W_inf_trial <- seq(from=0, to=12, by=0.1)
S <- 1/(1+exp(2.47+(0.386*Temp)-(16.8*pV_hy)))
B_msy <- 8.47*(D_mn*pV_eb*S)/(W_inf_trial^1.33)
M <- 0.26*(exp((0.021*Temp)+(0.0004*(Temp^2))))/(W_inf_trial^0.30)
msy_ha_samp <- B_msy*M
msy_samp <- msy_ha_samp*area   
# msy_n <- msy_samp/tbl6$W[tbl6$SW=="50/50"]
msy_n <- suppressWarnings(weighted_ests(msy_samp)$y_n)
 
par(mfrow=c(1,1))
par(family="serif")
plot(W_inf_trial, msy_n, type='l',
     xlab="Asymptotic Weight (kg)", ylab="MSY (n)",
     ylim=c(0, 2000), xlim=range(0, W_inf_trial))

# defining a sequence of trial values of W_inf to highlight
W_inf_trial <- c(W_inf_null, W_inf_samp, median(W_inf_mod))
S <- 1/(1+exp(2.47+(0.386*Temp)-(16.8*pV_hy)))
B_msy <- 8.47*(D_mn*pV_eb*S)/(W_inf_trial^1.33)
M <- 0.26*(exp((0.021*Temp)+(0.0004*(Temp^2))))/(W_inf_trial^0.30)
msy_ha_samp <- B_msy*M
msy_samp <- msy_ha_samp*area   
# msy_n <- msy_samp/tbl6$W[tbl6$SW=="50/50"]
msy_n <- suppressWarnings(weighted_ests(msy_samp)$y_n)

points(W_inf_trial, msy_n, pch=16)
segments(y0=msy_n, x0=-W_inf_trial, x1=W_inf_trial, lty=2)
segments(y0=msy_n, y1=-msy_n, x0=W_inf_trial, lty=2)

text(x=W_inf_trial, y=msy_n + c(20, 30, 120), pos=4,
     labels=paste0("W_inf = ", formatC(W_inf_trial, digits=2, format="f"), ",",
                   " MSY (n) = ", round(msy_n, 0)))
```

\pagebreak

### Both models, incorporating model error

```{r}
plot_fig45(tbl6, est=tbl7, ci=fig5_ci)
```

```{r, fig.width=10, fig.height=7}
par(mfrow=c(1,2))
plot_fig4(tbl6, cilim=c(0,3200))
plot_fig5(est=tbl7, ci=fig5_ci, cilim=c(0,3200))
```

### Both models, ignoring model error

```{r}
plot_fig45(tbl6_naive, est=tbl7, ci=fig5_ci_naive, cilim=200)
```

```{r, fig.width=10, fig.height=7}
par(mfrow=c(1,2))
plot_fig4(tbl6_naive, cilim=c(200, 850))
plot_fig5(est=tbl7, ci=fig5_ci_naive, cilim=c(200, 850))
```

```{r}
# p_winter <- seq(from=0, to=1, by=0.1)
# tbl7_null <- tbl7_samp <- tbl7_mod <- 
#   data.frame(`SW` = paste(100*(1-p_winter), 100*p_winter, sep="/"),
#              W=NA, SE_W=NA, 
#              MSY40=NA, MSY50=NA, MSY60=NA, MSY70=NA, MSY80=NA, MSY90=NA, MSY100=NA)
# for(i in 1:length(p_winter)) {
#   season_weights <- c(1-p_winter[i], p_winter[i])
#   tbl7_null$W[i] <- tbl7_samp$W[i] <- tbl7_mod$W[i] <-
#     sum(season_weights*season_Wbar)/sum(season_weights)
#   tbl7_null$SE_W[i] <- tbl7_samp$SE_W[i] <- tbl7_mod$SE_W[i] <-
#     sqrt(sum((season_weights^2)*season_varWbar)/(sum(season_weights)^2))
#   tbl7_null$MSY100[i] <- 
#     weighted_ests(y_kg=msy_null, season_weights=season_weights)$y_n
#   tbl7_samp$MSY100[i] <- 
#     weighted_ests(y_kg=msy_samp, season_weights=season_weights)$y_n
#   tbl7_mod$MSY100[i] <- 
#     weighted_ests(y_kg=msy_mod, season_weights=season_weights)$y_n
# }
# for(j in 4:9) {
#   tbl7_null[,j] <- j/10*tbl7_null[,10]
#   tbl7_samp[,j] <- j/10*tbl7_samp[,10]
#   tbl7_mod[,j] <- j/10*tbl7_mod[,10]
# }
```

```{r}
# p_msy <- seq(from=0.4, to=1, by=0.1)
# tbl8_null <- tbl8_samp <- tbl8_mod <- 
#   data.frame(perc_MSY=100*p_msy, MSY_n=NA, SE_MSY_n=NA, Upr_95_CI=NA, Lwr_95_CI=NA)
# for(i in 1:length(p_msy)) {
#   ests_null <- weighted_ests(y_kg=msy_null*p_msy[i])
#   ests_samp <- weighted_ests(y_kg=msy_samp*p_msy[i])
#   ests_mod <- weighted_ests(y_kg=msy_mod*p_msy[i])
#   
#   tbl8_null[i, 2:5] <- unlist(ests_null)
#   tbl8_samp[i, 2:5] <- unlist(ests_samp)
#   tbl8_mod[i, 2:5] <- unlist(ests_mod)
# }
```

```{r}
# # fig 5
# p_winter <- seq(from=0, to=1, by=0.01)
# fig5_null <- fig5_samp <- fig5_mod <- matrix(nrow=length(p_winter), ncol=4)
# for(i in 1:length(p_winter)) {
#   fig5_null[i,] <- 
#     unlist(weighted_ests(y_kg=0.5*msy_null, season_weights=c(p_winter[i], 1-p_winter[i])))
#   fig5_samp[i,] <- 
#     unlist(weighted_ests(y_kg=0.5*msy_samp, season_weights=c(p_winter[i], 1-p_winter[i])))
#   fig5_mod[i,] <- 
#     unlist(weighted_ests(y_kg=0.5*msy_mod, season_weights=c(p_winter[i], 1-p_winter[i])))
# }
# 
# plotfig5 <- function(x, ...) {
#   plot(x=p_winter, y=x[,1], ylim=range(x[,3:4]), type='l', xaxt="n", 
#        ylab="50% MSY (n)", xlab="Seasonal Weights", ...=...)
#   lines(x=p_winter, y=x[,3], lty=2)
#   lines(x=p_winter, y=x[,4], lty=2)
#   legend("topleft", lty=1:2, legend=c("Estimate", "95% CI"))
#   tlabs <- seq(from=0, to=1, by=0.2)
#   axis(side=1, at=tlabs, labels=paste0(100*tlabs, "% / ", 100*(1-tlabs), "%"))
# }
```

```{r}
# # fig 6
# p_MSY <- seq(from=0.4, to=1, by=0.01)
# fig6_null <- fig6_samp <- fig6_mod <- matrix(nrow=length(p_MSY), ncol=4)
# for(i in 1:length(p_MSY)) {
#   fig6_null[i,] <- 
#     unlist(weighted_ests(y_kg=p_MSY[i]*msy_null))
#   fig6_samp[i,] <- 
#     unlist(weighted_ests(y_kg=p_MSY[i]*msy_samp))
#   fig6_mod[i,] <- 
#     unlist(weighted_ests(y_kg=p_MSY[i]*msy_mod))
# }
# 
# plotfig6 <- function(x, ...) {
#   plot(x=p_MSY, y=x[,1], ylim=range(x[,3:4]), type='l', #xaxt="n", 
#        ylab="Fractional MSY (n)", xlab="Proportion of MSY", ...=...)
#   lines(x=p_MSY, y=x[,3], lty=2)
#   lines(x=p_MSY, y=x[,4], lty=2)
#   legend("topleft", lty=1:2, legend=c("Estimate", "95% CI"))
#   # tlabs <- seq(from=0, to=1, by=0.2)
#   # axis(side=1, at=tlabs, labels=paste0(100*tlabs, "% / ", 100*(1-tlabs), "%"))
# }
```


```{r}

# \pagebreak
# 
# ### Results with $W_{\infty}$ calculated from lake area (Lester equations)
# 
# ```{r}
# # dig7 <- c(0, 2, 2, rep(0, 7))
# # knitr::kable(tbl7_null, digits=dig7)
# ```
# 
# ```{r}
# # knitr::kable(tbl8_null, digits=0)
# ```
# 
# ```{r}
# # plotfig5(fig5_null)
# ```
# 
# ```{r}
# # plotfig6(fig6_null)
# ```
# 
# \pagebreak
# 
# ### Results with $W_{\infty}$ estimated from catch sampling
# 
# ```{r}
# # knitr::kable(tbl7_samp, digits=dig7)
# ```
# 
# ```{r}
# # knitr::kable(tbl8_samp, digits=0)
# ```
# 
# ```{r}
# # plotfig5(fig5_samp)
# ```
# 
# ```{r}
# # plotfig6(fig6_samp)
# ```
# 
# \pagebreak
# 
# ### Results with $W_{\infty}$ estimated using integrated Bayesian model
# 
# ```{r}
# # knitr::kable(tbl7_mod, digits=dig7)
# ```
# 
# ```{r}
# # knitr::kable(tbl8_mod, digits=0)
# ```
# 
# ```{r}
# # plotfig5(fig5_mod)
# ```
# 
# ```{r}
# # plotfig6(fig6_mod)
# ```

```
